Based on polling as of 27 October 2024, Harris expects to win on xxx%, leads Trump by xx% in 2024 US election

### 2024-10-30 paper/paper.qmd
update paper title

---
title: "Forecasting 2024 US election using linear regression"
author: 
  - Diana Shen
  - Jinyan Wei
  - Jerry Yu
thanks: "Code and data are available at: [https://github.com/DianaShen1224/Forecast-2024-US-election](https://github.com/DianaShen1224/Forecast-2024-US-election)."
date: today
date-format: long
abstract: "This paper predicts the outcome of the 2024 U.S. presidential election using a statistical model based on aggregated polling data for Kamala Harris and Donald Trump. We employ multi-level regression with post-stratification (MRP) using demographic predictors to estimate voter support. The analysis addresses polling biases and proposes an idealized survey methodology with a $100,000 budget. Our results offer insights into voter behavior and suggest improvements for future election forecasting models."
format: pdf
number-sections: true
bibliography: references.bib
editor: 
  markdown: 
    wrap: 72
---

@@

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

@@

## Analysis Data Summary Statistics

@tbl-analysisdata presents the summary statistics for each recorded
incident type for the years 2017 to 2022.

@@

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive
check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the
prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

@@

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

@@

6.  **How certain are you about your candidate choice?**

    -   Very certain
    -   Somewhat certain
    -   Not certain

@@

    Not important
    -   1
    -   2
    -   3
    -   4
    -   5
    Very important

>>>>

---
title: "Based on polling as of 27 October 2024, Harris expects to win on xxx%, leads Trump by xx% in 2024 US election"
subtitle: "Weighted Linear Regression Analysis of Aggregated Poll Data: Utilizing National Polls indicator, Recency of Polls, Sample Size, Pollster Quality Rate, and Poll Frequency as Predictors."
author: 
  - Diana Shen
  - Jinyan Wei
  - Jerry Yu
thanks: "Code and data are available at: [https://github.com/DianaShen1224/Forecast-2024-US-election](https://github.com/DianaShen1224/Forecast-2024-US-election)."
date: today
date-format: long
abstract: "This paper predicts the outcome of the 2024 U.S. presidential election using a statistical model based on aggregated polling data for Kamala Harris and Donald Trump. We employ multi-level regression with post-stratification (MRP) using demographic predictors to estimate voter support. The analysis addresses polling biases and proposes an idealized survey methodology with a $100,000 budget. Our results offer insights into voter behavior and suggest improvements for future election forecasting models."
format: pdf
number-sections: true
bibliography: references.bib
editor: 
  markdown: 
    wrap: 72
---

@@

first_model <-
  readRDS(file = here::here("models/model_unweighted.rds"))
```

@@

@@

## Model validation

```{r}
# Set seed for reproducibility
set.seed(123)

# Sample indices for training and testing sets
train_index <- sample(seq_len(nrow(data)), size = 0.8 * nrow(data))

# Split the data into training and testing sets
train_data <- data[train_index, ]
test_data <- data[-train_index, ]

# Fit the weighted linear regression model
first_model_test <- lm(pct ~ national_poll + pollster + population, 
                     data = data, 
                  data = train_data)

# Predict on test data
predictions <- predict(first_model_test, newdata = test_data)

# Calculate RMSE using the correct outcome variable
# Assuming 'pct' is the actual observed outcome variable in test_data
rmse <- sqrt(mean((predictions - test_data$pct)^2, na.rm = TRUE))

# Print RMSE
print(paste("RMSE:", rmse))

```

@@

@fig-stanareyouokay-1 is a residual plot of un-weighted model. It shows... This suggests...

@fig-stanareyouokay-2 is a Q-Q plot of un-weighted model plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2
#residual plot
plot(first_model, which = 1,main ="Residual Plot of unweighted linear regression model residualsmodel" )
# Q-Q plot for the residuals of the model
qqnorm(residuals(first_model),main= "Q-Q Plot of unweighted linear regression model residuals
")
qqline(residuals(first_model), col = "red")

```

@@

6.  **How likely are you going to vote in the 2024 election**

    Definitely not to vote

    -   1
    -   2
    -   3
    -   4
    -   5
    -   6
    -   7
    -   8
    -   9
    -   10 Definitely will vote

@@

    Not important

    -   1
    -   2
    -   3
    -   4
    -   5 Very important
